`r params$doc_title`

### 2023-03-13 scripts/MSc.Rmd
combine performance stats into list of dataframes per scenario

@@

filenamefig00_b <- paste0("../output/plots/", Sys.Date(), "_explained_var_X_new_sample_size_dep.png")
ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_new_PVE_X_formula.png")
ggsave(filename = filenamefig01_b, plot = fig01b.update, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

# SAVE
filenamefig02 <- paste0("../output/plots/", Sys.Date(), "_figure02.png")
ggsave(filename = filenamefig02, plot = fig02.update)
```

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!

filename_final_plot1 <- paste0("../output/plots/", Sys.Date(), "_final_plot1.arrange_OLD.png")
filename_final_plot1b <- paste0("../output/plots/", Sys.Date(), "_final_plot1b.arrange_NEW.png")

ggsave(filename = filename_final_plot1, plot = final_plot1.arrange, 
         width = 14, height = 10, 
         units = "in"  # default
         )
ggsave(filename = filename_final_plot1b, plot = final_plot1.arrange2, 
         width = 14, height = 10, 
         units = "in"  # default
         )
```

@@

```{r MendelianRandomization-analysis-GSD, warning=FALSE}
# outsourced calculation to `perform_mr.R`
# data FOR estimates in `perform_mr.R` script and simulation in `simstudy.R` script
saveRDS(my_data_harm, paste0("../output/Rdata/", Sys.Date(), "_my_data_harm.rds"))

@@

# SAVE
filename.mr.scatter.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrscatter_gsd.png")
ggsave(filename = filename.mr.scatter.gsd, plot = p1.gsd, 
         width = 10, height = 6, 
         units = "in"  # default
         )
```

@@

#SAVE
filename.mr.forest.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GSD.png")
ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
       width = 5, 
       height = 24, 
         #units = "in"  # default
         )
```

@@

#SAVE
filename.mr.funnel.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrfunnel_gsd.png")
ggsave(filename = filename.mr.funnel.gsd, plot = p4.gsd, 
       width = 8, 
       height = 4, 
       units = "in"  # default
         )

@@

# SAVE
filename.mr.scatter <- paste0("../output/plots/", Sys.Date(), "_figure_mrscatter.png")
ggsave(filename = filename.mr.scatter, plot = p1[[1]], 
         #width = 10, height = 6, 
         #units = "in"  # default
         )
```

@@

#SAVE
filename.mr.forest <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GBC.png")
ggsave(filename = filename.mr.forest, plot = p2[[1]], 
       width = 5, 
       height = 24, 
         #units = "in"  # default
         )
```

@@

#SAVE
filename.mr.funnel.gbc <- paste0("../output/plots/", Sys.Date(), "_figure_mrfunnel_gbc.png")
ggsave(filename = filename.mr.funnel.gbc, plot = p4, 
       width = 8, 
       height = 4, 
       units = "in"  # default
         )
```

@@

```{r simulatesimulatesimulate, warning=FALSE}
# save simulation-vars for simulation `simstudy.R` script
sim_vars <- list(n=n, colnames_pval=colnames_pval)
saveRDS(sim_vars, paste0("../output/Rdata/", Sys.Date(), "_sim_vars.rds"))
## SIMULATION OUTSOURCED TO "./scripts/simstudy.R"

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

@@

# EXPOSURE PVE
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim

@@

filename_pveplot_sim <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_pve.png")
ggsave(filename = filename_pveplot_sim, plot = plot_pve_simulated, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

filename_pveplot_sim.raincloud <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_pve_raincloud.png")
ggsave(filename = filename_pveplot_sim.raincloud, plot = plot_pve_simulated.raincloud, 
       width = 10, height = 6, 
       units = "in"  # default
       )
```

@@

```{r store-performance-metrics-csv}
## GSD
filename_IVW_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_IVW_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_MODE_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MODE_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_CONMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_CONMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
filename_MRMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MRMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
#5
filename_MEDIAN_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_MEDIAN_GSD_performance_metrics_NSIM_", nsim, ".csv")
#6
filename_EGGER_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_EGGER_GSD_performance_metrics_NSIM_", nsim, ".csv")
#7
filename_ROBUST_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_ROBUST_GSD_performance_metrics_NSIM_", nsim, ".csv")
#8
filename_PRESSO_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_PRESSO_GSD_performance_metrics_NSIM_", nsim, ".csv")
#9
filename_RAPS_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_RAPS_GSD_performance_metrics_NSIM_", nsim, ".csv")
#10
filename_LASSO_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
                                               Sys.Date(), "_LASSO_GSD_performance_metrics_NSIM_", nsim, ".csv")
write.csv2(x = IVW_GSD_performance_metrics, file = filename_IVW_GSD_performance_metrics)
write.csv2(x = MODE_GSD_performance_metrics, file = filename_MODE_GSD_performance_metrics)
write.csv2(x = CONMIX_GSD_performance_metrics, file = filename_CONMIX_GSD_performance_metrics)
write.csv2(x = MRMIX_GSD_performance_metrics, file = filename_MRMIX_GSD_performance_metrics)
#5
write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename_MEDIAN_GSD_performance_metrics)
#6
write.csv2(x = EGGER_GSD_performance_metrics, file = filename_EGGER_GSD_performance_metrics)
#7
write.csv2(x = ROBUST_GSD_performance_metrics, file = filename_ROBUST_GSD_performance_metrics)
#8
write.csv2(x = PRESSO_GSD_performance_metrics, file = filename_PRESSO_GSD_performance_metrics)
#9
write.csv2(x = RAPS_GSD_performance_metrics, file = filename_RAPS_GSD_performance_metrics)
#10
write.csv2(x = LASSO_GSD_performance_metrics, file = filename_LASSO_GSD_performance_metrics)
```

@@

# SAVE
filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
       width = 15, height = 6, 
       units = "in"  # default
       )
```

@@

filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_NSIM_", nsim,".png")
ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
       width = 10, height = 22, 
       units = "in"  # default
       )
```

@@

filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_NSIM_", nsim, ".png")
ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
       width = 7, height = 12, 
       units = "in"  # default
       )
```

@@

  # STORE
  filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_IVW_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
  filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_MODE_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
  filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
  filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)
  #5
  filename.MEDIAN_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_MEDIAN_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename.MEDIAN_table.performance)
  #6
  filename.EGGER_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_EGGER_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = EGGER_GSD_performance_metrics, file = filename.EGGER_table.performance)
  #7
  filename.ROBUST_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_ROBUST_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = ROBUST_GSD_performance_metrics, file = filename.ROBUST_table.performance)
  #8
  filename.PRESSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_PRESSO_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = PRESSO_GSD_performance_metrics, file = filename.PRESSO_table.performance)
  #9
  filename.RAPS_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_RAPS_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = RAPS_GSD_performance_metrics, file = filename.RAPS_table.performance)
  #10
  filename.LASSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                      "_LASSO_GSD_performance_metrics_TRUE_EST_", 
                                      selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  write.csv2(x = LASSO_GSD_performance_metrics, file = filename.LASSO_table.performance)

@@

  ggarrange(bias_mse_plot_IVW_GSD, bias_mse_plot_MODE_GSD, bias_mse_plot_CONMIX_GSD, bias_mse_plot_MRMIX_GSD, bias_mse_plot_MEDIAN_GSD,
            bias_mse_plot_EGGER_GSD, bias_mse_plot_ROBUST_GSD, bias_mse_plot_PRESSO_GSD, bias_mse_plot_RAPS_GSD, bias_mse_plot_LASSO_GSD,
            ncol = 1, nrow = 4, common.legend = TRUE) -> bias_mse_plot_GSD
  bias_mse_plot_GSD

  filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".png")
  ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
         width = 7, height = 12, 
         units = "in"  # default
         )
}
```

>>>>

SAVE.files <- FALSE

@@

if (SAVE.files ==TRUE ){
  filenamefig00_b <- paste0("../output/plots/", Sys.Date(), "_explained_var_X_new_sample_size_dep.png")
  ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
}

@@

if (SAVE.files ==TRUE ){
  filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_new_PVE_X_formula.png")
  ggsave(filename = filenamefig01_b, plot = fig01b.update, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

# SAVE
if (SAVE.files ==TRUE ){
  filenamefig02 <- paste0("../output/plots/", Sys.Date(), "_figure02.png")
  ggsave(filename = filenamefig02, plot = fig02.update)
}
```

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!
if (SAVE.files ==TRUE ){
  filename_final_plot1 <- paste0("../output/plots/", Sys.Date(), "_final_plot1.arrange_OLD.png")
  filename_final_plot1b <- paste0("../output/plots/", Sys.Date(), "_final_plot1b.arrange_NEW.png")

  ggsave(filename = filename_final_plot1, plot = final_plot1.arrange, 
           width = 14, height = 10, 
           units = "in"  # default
           )
  ggsave(filename = filename_final_plot1b, plot = final_plot1.arrange2, 
           width = 14, height = 10, 
           units = "in"  # default
           )
}
```

@@

```{r MendelianRandomization-analysis-GSD, warning=FALSE}
# outsourced calculation to `perform_mr.R`
# data FOR estimates in `perform_mr.R` script and simulation in `simstudy.R` script

if (SAVE.files ==TRUE ){
  saveRDS(my_data_harm, paste0("../output/Rdata/", Sys.Date(), "_my_data_harm.rds"))
}

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrscatter_gsd.png")
  ggsave(filename = filename.mr.scatter.gsd, plot = p1.gsd, 
           width = 10, height = 6, 
           units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GSD.png")
  ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrfunnel_gsd.png")
  ggsave(filename = filename.mr.funnel.gsd, plot = p4.gsd, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter <- paste0("../output/plots/", Sys.Date(), "_figure_mrscatter.png")
  ggsave(filename = filename.mr.scatter, plot = p1[[1]], 
           #width = 10, height = 6, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GBC.png")
  ggsave(filename = filename.mr.forest, plot = p2[[1]], 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gbc <- paste0("../output/plots/", Sys.Date(), "_figure_mrfunnel_gbc.png")
  ggsave(filename = filename.mr.funnel.gbc, plot = p4, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}
```

@@

```{r simulatesimulatesimulate, warning=FALSE}
# save simulation-vars for simulation `simstudy.R` script
sim_vars <- list(n=n, colnames_pval=colnames_pval)
if (SAVE.files ==TRUE ){
  saveRDS(sim_vars, paste0("../output/Rdata/", Sys.Date(), "_sim_vars.rds"))
}
## SIMULATION OUTSOURCED TO "./scripts/simstudy.R"

# read dat from "simstudy.R"  #------------------------------------------------
#est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_NSIM_", full.names = TRUE)))
# from "purrr-simstudy.R"
est_sim <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_purrr_NSIM_", full.names = TRUE)))
est_sim_architectures <- readRDS(dplyr::last(list.files(path = "../output/Rdata", pattern = "_est_sim_architectures_purrr_NSIM_", full.names = TRUE)))
nsim <- nrow(est_sim)
```

@@

# EXPOSURE PVE ------------------------------------------------------------------------------------------------------
est_sim %>% 
  select(!!!(colname_pve_X)) %>% 
  pivot_longer(everything(), names_to = "PVE_X", values_to = "value_X") %>% 
  cbind(sample_size_filtered) %>% as_tibble() -> pve_X_sim

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_pve.png")
  ggsave(filename = filename_pveplot_sim, plot = plot_pve_simulated, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim.raincloud <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_pve_raincloud.png")
  ggsave(filename = filename_pveplot_sim.raincloud, plot = plot_pve_simulated.raincloud, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

```{r store-performance-metrics-csv}
## GSD  we loop in the next section and save the files there with all references!
# filename_IVW_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_IVW_GSD_performance_metrics_NSIM_", nsim, ".csv")
# filename_MODE_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_MODE_GSD_performance_metrics_NSIM_", nsim, ".csv")
# filename_CONMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_CONMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
# filename_MRMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_MRMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #5
# filename_MEDIAN_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_MEDIAN_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #6
# filename_EGGER_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_EGGER_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #7
# filename_ROBUST_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_ROBUST_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #8
# filename_PRESSO_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_PRESSO_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #9
# filename_RAPS_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_RAPS_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #10
# filename_LASSO_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_LASSO_GSD_performance_metrics_NSIM_", nsim, ".csv")
# write.csv2(x = IVW_GSD_performance_metrics, file = filename_IVW_GSD_performance_metrics)
# write.csv2(x = MODE_GSD_performance_metrics, file = filename_MODE_GSD_performance_metrics)
# write.csv2(x = CONMIX_GSD_performance_metrics, file = filename_CONMIX_GSD_performance_metrics)
# write.csv2(x = MRMIX_GSD_performance_metrics, file = filename_MRMIX_GSD_performance_metrics)
# #5
# write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename_MEDIAN_GSD_performance_metrics)
# #6
# write.csv2(x = EGGER_GSD_performance_metrics, file = filename_EGGER_GSD_performance_metrics)
# #7
# write.csv2(x = ROBUST_GSD_performance_metrics, file = filename_ROBUST_GSD_performance_metrics)
# #8
# write.csv2(x = PRESSO_GSD_performance_metrics, file = filename_PRESSO_GSD_performance_metrics)
# #9
# write.csv2(x = RAPS_GSD_performance_metrics, file = filename_RAPS_GSD_performance_metrics)
# #10
# write.csv2(x = LASSO_GSD_performance_metrics, file = filename_LASSO_GSD_performance_metrics)
```

@@

# # SAVE   # we loop in the next section and save the ggarrange plots for inspection
# filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_NSIM_", nsim,".png")
# ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
#        width = 15, height = 6, 
#        units = "in"  # default
#        )
# filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_NSIM_", nsim,".png")
# ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
#        width = 15, height = 6, 
#        units = "in"  # default
#        )
# filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_NSIM_", nsim,".png")
# ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
#        width = 15, height = 6, 
#        units = "in"  # default
#        )
# filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_NSIM_", nsim,".png")
# ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
#        width = 15, height = 6, 
#        units = "in"  # default
#        )
```

@@

if (SAVE.files ==TRUE ){
  filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_NSIM_", nsim,".png")
  ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
         width = 10, height = 22, 
         units = "in"  # default
         )
}
```

@@

if (SAVE.files ==TRUE ){
  filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_NSIM_", nsim, ".png")
  ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
         width = 7, height = 12, 
         units = "in"  # default
         )
}
```

@@

  # #----
  # COMBINE TO PRESENT RESULTS ----------------------------------------------------
  # #----
  df_name <- paste0("df_combined_method_metrics_TRUE_EST_", selected_true_methods[true_method])
  assign(x = df_name, value = tibble(N=n))
  # scenarios <- c("all_instruments", "common_strong", "common_weak", "rare_strong", "rare_weak")
  assign(x = df_name, value = eval(as.symbol(df_name)) %>% 
    left_join(IVW_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(MODE_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(CONMIX_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(MRMIX_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(MEDIAN_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(EGGER_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(ROBUST_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(PRESSO_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(RAPS_GSD_performance_metrics %>% select(-var), by = c("N"="N")) %>% 
    left_join(LASSO_GSD_performance_metrics %>% select(-var), by = c("N"="N"))
  )
  #eval(as.symbol(df_name))

  # STORE
  if (SAVE.files ==TRUE ){
    filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_IVW_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
    filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_MODE_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
    filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
    filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)
    #5
    filename.MEDIAN_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_MEDIAN_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename.MEDIAN_table.performance)
    #6
    filename.EGGER_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_EGGER_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = EGGER_GSD_performance_metrics, file = filename.EGGER_table.performance)
    #7
    filename.ROBUST_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_ROBUST_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = ROBUST_GSD_performance_metrics, file = filename.ROBUST_table.performance)
    #8
    filename.PRESSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_PRESSO_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = PRESSO_GSD_performance_metrics, file = filename.PRESSO_table.performance)
    #9
    filename.RAPS_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_RAPS_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = RAPS_GSD_performance_metrics, file = filename.RAPS_table.performance)
    #10
    filename.LASSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_LASSO_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = LASSO_GSD_performance_metrics, file = filename.LASSO_table.performance)
  }

@@

  ggarrange(bias_mse_plot_IVW_GSD, bias_mse_plot_MODE_GSD, bias_mse_plot_CONMIX_GSD, bias_mse_plot_MRMIX_GSD, bias_mse_plot_MEDIAN_GSD,
            bias_mse_plot_EGGER_GSD, bias_mse_plot_ROBUST_GSD, bias_mse_plot_PRESSO_GSD, bias_mse_plot_RAPS_GSD, bias_mse_plot_LASSO_GSD,
            ncol = 1, nrow = 10, common.legend = TRUE) -> bias_mse_plot_GSD
  bias_mse_plot_GSD

  if (SAVE.files ==TRUE ){
    filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".png")
    ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
           width = 7, height = 24, 
           units = "in"  # default
           )
  }
}

## Now loop over all genetic architecture simulations

```{r parallel-performance-genetic-architectures}
effect_size <- c("strong", "weak")
maf <- c("rare", "common")
all_quadrants <- tidyr::crossing(effect_size, maf)

# create copy of est_sim so the genetic architectures can be assigned to this variable in the loop 
# without losing the simulations on all variants not considering genetic architecture
est_sim_all_variants <- est_sim

# now we do not need to rewrite the code from above but can assign each genetic architecture df to  est_sim
# and only need to change the names of the files we store for later usage
for (my_architecture in 1:length(est_sim_architectures)) {

  est_sim <- est_sim_architectures[[my_architecture]]
  name_GenArch <- gsub(pattern = "_est_sim", replacement = "", names(est_sim_architectures)[my_architecture])

  # fewer variants -> no results for smaller sample sizes -> reassign sample sizes and colnames
